---
title: "Homework 10"
author: "Marley McGehee"
date: "4/15/2026"
output:  
  html_document:
    code_folding: hide

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
library(Lock5Data)
library(tidyverse)
library(lubridate)

```


## General Social Survey

### Marital Status
```{r}
gss_cat_mar <- gss_cat %>% 
  mutate(marital = fct_collapse(marital,
"Pre Marriage" = c("Never married"),
"Marriage" = c("Married", "Separated"),
"Post Marriage" = c("Divorced", "Widowed"),
"Missing" = c("No answer")
)) 


knitr::kable(gss_cat_mar %>% 
  count(marital))
```

^[Question 1 complete]



```{r}
gss_cat_prop <- gss_cat_mar %>%
  count(year, marital) %>%
  group_by(year) %>%
  mutate(proportion = n / sum(n))
```

^[Question 2 Complete]

```{r}
gss_cat_prop_order <- gss_cat_prop %>%
  arrange(desc(year))


```
^[Question 3 Complete]

```{r}
ggplot(gss_cat_prop_order, aes(y = proportion, x = year, color = marital)) +
  geom_line()
```
^[Question 4 complete]

## Los Angeles Lakers

```{r}

knitr::kable(lubridate::lakers %>% 
               mutate(date = as_date(date))%>%
               select(date, opponent, game_type, time) %>%
               head(n = 6))
```

The date data is wrong, because when converting directly from integer to date it is reading the date as a singular number instead of a date. While we can see that the date is an actual date not separated by slashes, by using the as_date command it ends up viewing the initial date as days and adding them to 1970-01-01.^[Question 1 complete]


```{r}
lakers_new <-lubridate::lakers %>% 
               mutate(date = ymd(date))
               
knitr::kable(lakers_new %>%
               select(date, opponent, game_type, time) %>%
               head(n = 6))

```

This works better because you are telling it to read the date data as a year, month, and day. By telling it the specific values it is reading it helps it know how to convert it. ^[Question 2 complete]

```{r}
distinct_lakers <- lakers_new %>%
  distinct(date) %>%
  mutate(day_of_week = wday(date, label = TRUE, abbr = FALSE))

ggplot(distinct_lakers, aes(x = day_of_week )) +
  geom_bar() +
  labs(x = "Day of Week")
```

^[Question 3 complete]